---
title: "Module 2 Individual Assignment"
author: "Kiran Kasu"
date: '2022-04-23'
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```


```{r}
#Loading the libraries
library(ggplot2)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(leaps)
library(ggthemes)
library(car)
library(corrplot)
library(gridExtra)
```


#Task 1
```{r}
GP1 <- c(0.2, 0.28, 0.36, 0.16)
OS1 <- c(12, 8, 24, 6)

bloodtype_df <- data.frame(GP1,OS1)
row.names(bloodtype_df) <- c("Type_A","Type_B","Type_O", "Type_AB")
bloodtype_df

alpha_95 = 0.05
CV1 <- qchisq(p=0.05, df=3,lower.tail = F)
cat("\nCritical Value For Alpha=0.05 and df=3 is",CV1,"\n")

alpha_90 = 0.10
CV2 <- qchisq(p=0.10, df=3,lower.tail = F)
cat("\nCritical Value For Alpha=0.01 and df=3 is",CV2,"\n")

#Test Statistics
test1 <- chisq.test(x=OS1,p=GP1)
test1$statistic
p1 <- test1$p.value
p1

ifelse(p1 > alpha_95, "Fail to reject H0","Reject H0")
ifelse(p1 > alpha_90, "Fail to reject H0","Reject H0")
```
#Task 2
```{r}
OT1 <- c(0.708, 0.082, 0.09, 0.12)
RS1 <- c(125,10,25,40)

OTE_DF <- data.frame(OT1,RS1)
row.names(OTE_DF) <- c("On_time","NAS_Delay","Aircraft_Arriving_Late","Others[Weather]")
OTE_DF

alpha_95 = 0.05
CV1 <- qchisq(p=0.05, df=3,lower.tail = F)
cat("\nCritical Value For Alpha=0.05 and df=3 is",CV1,"\n")

#Test statistics
test2 <- chisq.test(x=RS1,p=OT1)
test2$statistic
p2 <-test2$p.value

ifelse(p2 > alpha_95, "Fail to reject H0","Reject H0")
```

#Task 3
```{r}
X1<- c(724,335,174,107)
X2<- c(370,292,152,140)

#Creating a matrix
matrix1= matrix(c(X1,X2), nrow=2,byrow=TRUE)
matrix1

rownames(matrix1)<-c("2013","2014")
colnames(matrix1)<-c("Caucasian","Hispanic","African_American","Other")
matrix1

# Critical value

alpha_95 = 0.05
CV1 <- qchisq(0.05, 3,lower.tail = F)
cat("\nCritical Value For Alpha=0.05 and df=3 is",CV1,"\n")

test3 <-chisq.test(matrix1)
test3
p3 <- test3$p.value

ifelse(p3 > alpha_95, "Fail to reject H0","Reject H0")
```

#Task 4
```{r}
RM1 <- c(10791, 7816, 932, 11819)
RM2 <- c(62491, 42750, 9525, 54344)

#Creating the matrix
matrix_2= matrix(c(RM1,RM2),nrow=4,byrow=F)
matrix_2

rownames(matrix_2)<-c("Army", "Navy", "Marine_Corps", "Air_Force")
colnames(matrix_2)<-c("OFFICERS","ENLISTED")
matrix_2

alpha_95 = 0.05
CV1 <- qchisq(0.05, 3,lower.tail = F)
cat("\nCritical Value For Alpha=0.05 and df=3 is",CV1,"\n")


test_4 <- chisq.test(matrix_2)
test_4
p4 <- test_4$p.value
p4

# making the decision by comparing p-value with alpha value
ifelse(p4 > alpha_95, "Fail to reject H0","Reject H0")
```


#Task 5
```{r}
alpha_95= 0.05

Condi<- data.frame('Sodium_in_mg'=c(270,130,230,180,80,70,200),'Nutriment'=rep('Condiment',7),stringsAsFactors=F)
cereal<- data.frame('Sodium_in_mg'=c(260,220,290,290,200,320,140),'Nutriment'=rep('cereals',7), stringsAsFactors=F)
Dessert<- data.frame('Sodium_in_mg'=c(100,180,250,250,300,360,300),'Nutriment'=rep('Dessert',7),stringsAsFactors=F)


sodium <- rbind(Condi,cereal,Dessert)
sodium$Nutriment <- as.factor(sodium$Nutriment)

# ANOVA TEST
test5 <-aov(Sodium_in_mg ~ Nutriment,data=sodium)
test5_summary <- summary(test5)

freedom <- test5_summary[[1]][1,"Df"]
freedom

freedom_error <- test5_summary[[1]][2,"Df"]
freedom_error


squaretreatment <- test5_summary[[1]][1,"Sum Sq"]
squaretreatment

square_error <- test5_summary[[1]][2,"Sum Sq"]
square_error

# F test Statistic
QT1 <- squaretreatment/freedom
QT2 <- square_error/freedom_error
F_value <- QT1/QT2
cat("F-Statistic is",F_value,"\n")

# P Value for F statistic
p5<- test5_summary[[1]][[1,"Pr(>F)"]]
cat("P-Value is",p5,"\n")


ifelse(p5 > alpha_95, "Fail to reject H0","Reject H0")

# calculating differences
TukeyHSD(test5)     
```

#Test 6
```{r}
# Creating Data Frames
Cereal<-data.frame('Sale_in_millions'=c(578,320,264,249,237),'Nutriment'=rep('Cereal',5),stringsAsfactors=FALSE)
candy<-data.frame('Sale_in_millions'=c(311,106,109,125,173),'Nutriment'=rep('candy',5),stringsAsfactors=FALSE)
Coffee<-data.frame('Sale_in_millions'=c(261,185,302,689),'Nutriment'=rep('Coffee',4),stringsAsfactors=FALSE)

# Combining the Data Frames using rbind function
DF1 <- rbind(Cereal,candy,Coffee)
DF1$Nutriment <- as.factor(DF1$Nutriment)
DF1

# performing ANOVA Test
test6 <-aov(Sale_in_millions ~ Nutriment,data=DF1)
test6_summary <- summary(test6)

freedom <- test6_summary[[1]][1,"Df"]
freedom

freedom_error <- test6_summary[[1]][2,"Df"]
freedom_error

#calculating the Sum of squares 
square_treat <- test6_summary[[1]][1,"Sum Sq"]
square_treat

#calculating the Sum of squares of Error
square_error <- test6_summary[[1]][2,"Sum Sq"]
square_error

# calculating Ftest Statistic 
QT1 <- square_treat/freedom
QT2 <- square_error/freedom_error
F_value <- QT1/QT2
cat("F-Statistic is",F_value,"\n")

# calculating the P_Value for F statistic
p6<- test6_summary[[1]][[1,"Pr(>F)"]]
cat("P-Value is",p6,"\n")

alpha99 = 0.01
# making the decision by comparing p-value with alpha value
ifelse(p6 > alpha99, "Fail to reject H0","Reject H0")

# calculating differences 
TukeyHSD(test6)
```

#Test 7
```{r}
# Creating Data Frames using data.frame
Eastern<-data.frame('Pupil_Exp'=c(4946,5953,6202,7243,6113),'Region'=rep('Easthernt_Third',5),stringsAsfactors=FALSE)
Middle<-data.frame('Pupil_Exp'=c(6149,7451,6000,6479),'Region'=rep('Middle_Third',4),stringsAsfactors=FALSE)
Western<-data.frame('Pupil_Exp'=c(5282,8605,6528,6911),'Region'=rep('Western_Third',4),stringsAsfactors=FALSE)

# Combining three Data Frames using rbind function
pupil<-rbind(Eastern,Middle,Western)
pupil$Region<-as.factor(pupil$Region)
pupil

# performing the ANOVA Test
test7 <-aov(Pupil_Exp ~ Region,data=pupil)
test7_summary <- summary(test7)
test7_summary

# calculating Degrees Of Freedom
freedom <- test7_summary[[1]][1,"Df"]
freedom
#calculating the Degrees Of Freedom for error
freedom_error <- test7_summary[[1]][2,"Df"]
freedom_error

#calculating Sum of squares 
square_treat <- test7_summary[[1]][1,"Sum Sq"]
square_treat
#calculating the Sum of squares
square_error <- test7_summary[[1]][2,"Sum Sq"]
square_error

# performing the Ftest Statistic 
QT1 <- square_treat/freedom
QT2 <- square_error/freedom_error
F_value <- QT1/QT2
cat("F-Statistic is",F_value,"\n")
# calculating P_Value for F statistic
p7<- test7_summary[[1]][[1,"Pr(>F)"]]
cat("P-Value is",p7,"\n")

alpha_95 = 0.05
# making the decision by comparing p-value with alpha value
ifelse(p7 > alpha_95, "Fail to reject H0","Reject H0")

# calculating differences  by performing tukey test
TukeyHSD(test7)      

```

#Task 8
```{r}
FA_L1 <- c(9.2,9.4,8.9)
FA_L2 <- c(8.5,9.2,8.9)
FB_L1 <-c(7.1,7.2,8.5)
FB_L2 <- c(5.5,5.8,7.6)

# Creating Data Frame
Plants_DF <- as.data.frame(matrix(c(rep("FoodA",3), rep("FoodA",3), rep("FoodB", 3), rep("FoodB", 3), rep("Light1",3), rep("Light2",3), rep("Light1",3), rep("Light2", 3), FA_L1, FA_L2, FB_L1, FB_L2),ncol = 3))
names(Plants_DF) <- c('Food_Type','Light_Type', 'Growth_In_Inches')

Plants_DF$Growth_In_Inches <- as.numeric(as.character(Plants_DF$Growth_In_Inches))

# Anova Test
T8_Result <- aov( Growth_In_Inches ~ Food_Type * Light_Type, data = Plants_DF)
summary(T8_Result)

RM1_p <- round(summary(T8_Result)[[1]][1,"Pr(>F)"],4)
RM2_p <- round(summary(T8_Result)[[1]][2,"Pr(>F)"],4)
C3_p <- round(summary(T8_Result)[[1]][3,"Pr(>F)"],4)

alpha_95 = 0.05
#decision making
ifelse(RM1_p > alpha_95, "Fail to reject claim-1 H0","Reject Claim-1 H0")
ifelse(RM2_p > alpha_95, "Fail to reject claim-2 H0","Reject Claim-2 H0")
ifelse(C3_p > alpha_95, "Fail to reject claim-3 H0","Reject Claim-3 H0")

```

#Task 9 
```{r}
baseball <- read.csv("C:\\Users\\kasuk\\OneDrive\\Documents\\baseball.csv")
View(baseball)

psych::describe(baseball)
```


```

```{r}
#Finding the critical Value using qchisq function
alpha_95 = 0.05
CV1 <- qchisq(p=0.05, df=5,lower.tail = F)
CV1

OB <- c(13267, 17934, 18926, 17972, 24286, 7289)
EX <- c(1/6,1/6,1/6,1/6,1/6,1/6)

test_9.1 <-chisq.test(OB,p=EX)
test_9.1


# making the decision by comparing p-value with alpha value
ifelse(test_9.1$p.value > alpha_95, "Fail to reject H0","Reject H0")


```


#Task 9.2
```{r}
# Importing the crop_data-set using read.csv function
crop <- read.csv("C:\\Users\\kasuk\\OneDrive\\Documents\\crop_data.csv")
psych::describe(crop)

# performing the ANOVA Test
test_9.2 <-  aov(yield ~ (density * fertilizer),data = crop)
summary(test_9.2)

p1 <- summary(test_9.2)[[1]][1,"Pr(>F)"]
p2 <- summary(test_9.2)[[1]][2,"Pr(>F)"]
p3 <- summary(test_9.2)[[1]][3,"Pr(>F)"]

alpha_95 = 0.05
# making the decision by comparing p-value with alpha value
ifelse(p1 > alpha_95, "Fail to reject claim-1 H0","Reject Claim-1 H0")
ifelse(p2 > alpha_95, "Fail to reject claim-2 H0","Reject Claim-2 H0")
ifelse(p3 > alpha_95, "Fail to reject claim-3 H0","Reject Claim-3 H0")


```


